### 2018-11-04 Sections/about_the_authors.tex

>>>>

%
% Chandra Radhakrishnan 
%

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_chandra_radhakrishnan}
\end{center}

Chandrashekar Radhakrishnan is a Postdoctoral Fellow and Bright Overseas Global Corporation Scholar at New York University, Shanghai, Chibna. He is a recipient of the National Natural Science Foundation of China, International Young Scientist research grant. Before Joining NYU Shanghai he worked as a Postdoctoral Fellow at the Institute of Mathematical Science, India and the National Chung Hsing University, Taiwan. He obtained his Master of Science in Physics from the Indian Institute of Technology Madras and a PhD in theoretical physics from University of Madras. He has worked on a variety of fields, including statistical mechanics, mathematical physics and quantum information theory. His fundamental interest in quantum information theory lies in investigating quantum resources alternative to entanglement, which can be used for quantum communication and quantum computation. He has active collaborations with experimentalists, through which he tries to verify his theoretical results. He also has some interest in the application of statistical mechanics to biological problems.

### 2018-11-04 Sections/cloud_quantum_computing.tex
Tiny

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{patchwork_cluster} 
\captionspacefig \caption{Approach for constructing distributed cluster states across multiple nodes. The quantum channels allow neighbouring clusters in the topology to be fused together, constructing a large virtual cluster state for distributed computation. The nodes could be arbitrarily separated with optically-mediated interconnects to enable fusing nodes together.} \label{fig:patchwork_cluster}
\end{figure}

@@

\subsection{The globally unified quantum cloud}\index{Globally unified quantum cloud}

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{patchwork_cluster} 
\captionspacefig \caption{Approach for constructing distributed cluster states (or topological codes, or other graph states) across multiple nodes. The quantum channels allow neighbouring clusters in the topology to be fused together, constructing a large virtual cluster state for distributed computation. The nodes could be arbitrarily separated with optically-mediated interconnects to enable fusing nodes together.} \label{fig:patchwork_cluster}
\end{figure}

@@

\subsection{The globally unified quantum cloud}\index{Globally unified quantum cloud}\label{sec:glob_unif_quant_cloud}

### 2018-11-04 Sections/economics_of_the_quantum_internet.tex

\begin{itemize}
\item Subjective value of computation: the value to an end-user of a computation, measured in terms of their associated monetary profit from utilising its output, which is highly application-specific.
\item Objective value of computation: the cost of the physical hardware and infrastructure, which is not application-specific.
\end{itemize}

This effectively implies that some users pay more for computation (in terms of return on investment\index{Return on investment (RoI)}) than others. While the objective cost of computation is conceptually simple to model (as performed in a rudimentary fashion in Sec.~\ref{sec:cost_of_comp}), the subjective cost is a highly non-trivial one. It will depend heavily on the scaling function of the algorithm run by a user, and of course the economic objectives of their computation -- a quantum simulation algorithm executed by an R\&D lab\index{R\&D} is likely to be of greater monetary value than and undergrad using his university's resources for completing an assignment!

@@

>>>>

\begin{itemize}
\item Subjective value of computation: the value to an end-user of a computation, measured in terms of their associated monetary profit from utilising its output, which is highly application-specific.
\item Objective value of computation: the cost of the physical hardware and infrastructure, which is not application-specific, but rather stipulated by technological and manufacturing progress.
\end{itemize}

This effectively implies that some users pay more for computation (in terms of return on investment\index{Return on investment (RoI)}) than others. While the objective cost of computation is conceptually simple to model (as performed in a rudimentary fashion in Sec.~\ref{sec:cost_of_comp}), the subjective cost is a highly non-trivial one. It will depend heavily on the scaling function of the algorithm run by a user, and of course the economic objectives of their computation -- a quantum simulation algorithm executed by an R\&D lab\index{R\&D} is likely to be of greater monetary value than and undergrad using his university's resources to execute the same task for completing an assignment!

@@

%
% Geographic Localisation
%

\subsection{Geographic localisation}\index{Geographic localisation}\label{sec:geo_loc}

Because of the resource overheads associated with performing computations in a distributed manner, e.g via the resource costs associated with long-range repeater networks\index{Quantum repeater networks}, there is an economic imperative to localise quantum infrastructure, so as to mitigate this -- there is a clear economic benefit associated with housing qubits in close geographic proximity such that no long-distance quantum channels are required.

However, it's undesirable to \textit{entirely} centralise infrastructure of \textit{any} type, for two primary reasons:
\begin{itemize}
	\item Geo-strategic competition\index{Geo-strategic politics}: competing nation states or enterprises may not want essential infrastructure to be located entirely offshore, placing them at the mercy of their strategic competitors.
	\item Geographical redundancy\index{Geographical redundancy}: to eliminate single points of failure\index{Single points of failure} (SPOF), which undermine network robustness, it's desirable for infrastructure to be geographically decentralised. In present-day large-scale distributed classical platforms, geographical redundancy is a key consideration. Even though it would be most efficient if all data were completely centralised, obviating communications overheads, it would be catastrophic if a single earthquake (or war!) could decimate the entire system.
\end{itemize}

Thus, we can reasonably anticipate that the quantum internet will not evolve like the classical `internet of things'\index{Internet of things}, whereby a massive number of ultra-small computational resources are scattered across the globe and networked. Rather, a relatively small number of central `hubs'\index{Hubs} are likely to emerge, which centralise enormous computational power, interconnected via the quantum internet to form the globally unified quantum cloud (Sec.~\ref{sec:glob_unif_quant_cloud}).

Much like the classical internet, it's to be expected the network that will emerge will approximate a scale-free network (Sec.~\ref{sec:scale_free_networks})\index{Scale-free networks}, with a very hierarchical structure, following a Pareto distribution\index{Pareto distribution} in hub-size.

### 2018-11-04 Sections/essay_NISQ_QC.tex

\begin{itemize}
\item Quantum complexity: we have strong reason to believe that some tasks efficient on quantum computers may be computationally difficult classically. The best-known example is Shor's algorithm \cite{bib:shor1994algorithms}, allowing us to factorise large numbers exponentially  faster than using the best classical methods. Whilst we do not have a proof that an efficient classical algorithm doesn't exist, the brightest of mathematicians have been trying to find one for decades to no avail. Integer factorisation has significant implications for cryptography, where the security of some codes is underpinned by the believed computational complexity of this particular problem. 
\item Complexity theory arguments: computer scientists have shown that quantum states which can be easily prepared with a quantum computer have super-classical properties. For example, given single photons input into a multi-mode interferometer, it's hard for a classical computer to sample the probability distribution at the output, the so-called {\sc BosonSampling} problem\index{Boson-sampling}. On the other hand, a quantum computer can trivially implement this experiment.
\item No known classical algorithm can efficiently simulate a universal, fault-tolerant quantum computer, or simulate general quantum systems.
\end{itemize}

>>>>

\begin{itemize}
\item Quantum complexity: we have strong reason to believe that some tasks efficient on quantum computers may be computationally difficult classically. The best-known example is Shor's algorithm \cite{bib:ShorFactor}, allowing us to factorise large numbers exponentially  faster than using the best classical methods. Whilst we do not have a proof that an efficient classical algorithm doesn't exist, the brightest of mathematicians have been trying to find one for decades to no avail. Integer factorisation has significant implications for cryptography, where the security of some codes is underpinned by the believed computational complexity of this particular problem. 
\item Complexity theory arguments: computer scientists have shown that quantum states which can be easily prepared with a quantum computer have super-classical properties. For example, given single photons input into a multi-mode interferometer, it's hard for a classical computer to sample the probability distribution at the output, the so-called {\sc BosonSampling} problem\index{Boson-sampling}. On the other hand, a quantum computer can trivially implement this experiment.
\item No known classical algorithm can efficiently simulate a universal, fault-tolerant quantum computer, or simulate general quantum systems.
\end{itemize}

### 2018-11-04 Sections/foreword.tex

A basic understanding of quantum mechanics \cite{bib:Sakurai94}, quantum optics \cite{bib:GerryKnight05}, quantum computing and quantum information theory \cite{bib:NielsenChuang00}\footnote{Throughout this manuscript we use the Nielsen \& Chuang convention for the pronunciation of `zed' \cite{bib:NielsenChuang00}.\index{Zed}}, and classical networking \cite{bib:TanenbaumNet} are helpful, but not essential, to following our discussion. Some mathematical sections require a basic understanding of the mathematical notation of quantum mechanics. Although the reader without this background ought to be able to nonetheless follow the broader arguments.

>>>>

A basic understanding of quantum mechanics \cite{bib:Sakurai94}, quantum optics \cite{bib:GerryKnight05}, quantum computing and quantum information theory \cite{bib:NielsenChuang00}\footnote{Throughout this manuscript we use the Nielsen \& Chuang convention for the pronunciation of `zed' \cite{bib:NielsenChuang00}.\index{Zed}}, classical networking \cite{bib:TanenbaumNet}, and computer algorithms \cite{bib:RivestAlgBook} are helpful, but not essential, to following our discussion. Some mathematical sections require a basic understanding of the mathematical notation of quantum mechanics. Although the reader without this background ought to be able to nonetheless follow the broader arguments.

### 2018-11-04 Sections/introduction.tex

Perhaps the most exciting prospect in the quantum age is the development of quantum computers\index{Quantum computing}. Richard Feynman \cite{bib:Feynman85} was the first to ask the question ``If quantum systems are so exponentially complex that we are unable to simulate them on our classical computers, can those same quantum systems be exploited in a controlled way to exponentially outperform our classical computers?"\index{Richard Feynman}. Subsequently, the Deutsch-Jozsa algorithm \cite{bib:DeutschJozsa92}\index{Deutsch-Jozsa algorithm} demonstrated for the first time that algorithms can run on a quantum computer, exponentially outperforming any classical algorithm. Since then, an enormous amount of research has been dedicated to finding new quantum algorithms, and the search has indeed been a very fruitful one\footnote{See the Quantum Algorithm Zoo\index{Quantum Algorithm Zoo} for a comprehensive summary of the current state of knowledge on quantum algorithms (\href{http://math.nist.gov/quantum/zoo/}{http://math.nist.gov/quantum/zoo/}).}, with many important applications having been found, including, amongst many others\index{Quantum algorithms}:

>>>>

Perhaps the most exciting prospect in the quantum age is the development of quantum computers\index{Quantum computing}. Richard Feynman \cite{bib:Feynman85} was the first to ask the question \textit{``If quantum systems are so exponentially complex that we are unable to simulate them on our classical computers, can those same quantum systems be exploited in a controlled way to exponentially outperform our classical computers?"}\index{Richard Feynman}. Subsequently, the Deutsch-Jozsa algorithm \cite{bib:DeutschJozsa92}\index{Deutsch-Jozsa algorithm} demonstrated for the first time that algorithms can run on a quantum computer, exponentially outperforming any classical algorithm. Since then, an enormous amount of research has been dedicated to finding new quantum algorithms, and the search has indeed been a very fruitful one\footnote{See the Quantum Algorithm Zoo\index{Quantum Algorithm Zoo} for a comprehensive summary of the current state of knowledge on quantum algorithms (\href{http://math.nist.gov/quantum/zoo/}{http://math.nist.gov/quantum/zoo/}).}, with many important applications having been found, including, amongst many others\index{Quantum algorithms}:

### 2018-11-04 Sections/network_topologies.tex
Adding image cropping

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{K_15}
\captionspacefig \caption{The 15-vertex complete graph, $K_{15}$. Every vertex has an edge to every other, with a total of 105 edges.} \label{fig:complete_graph}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{lattice}
\captionspacefig \caption{A \mbox{$10\times 11$} square lattice graph, and how it might represent a network topology with geographically associated costs. Notice that Hobart has no internet connection (why even include Tasmania at all?).} \label{fig:lattice}
\end{figure}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.325\textwidth]{tree_3_8}\\
	\includegraphics[width=0.325\textwidth]{tree_4_8}\\
	\includegraphics[width=0.325\textwidth]{tree_5_8}
	\captionspacefig \caption{Balanced tree graphs with branching factor \mbox{$b=8$}, and depths \mbox{$d=3,4,5$}. Despite having no redundant paths, the hierarchical structure of balanced trees somewhat resembles that of real-world networks, which are typically decomposed into a pyramid scheme of progressively smaller subnetworks.} \label{fig:tree_example}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.325\textwidth]{tree_3_8}
	\includegraphics[width=0.325\textwidth]{tree_4_8}
	\includegraphics[width=0.325\textwidth]{tree_5_8}
	\captionspacefig \caption{Balanced tree graphs with branching factor \mbox{$b=8$}, and depths \mbox{$d=3,4,5$}. Despite having no redundant paths, the hierarchical structure of balanced trees somewhat resembles that of real-world networks, which are typically decomposed into a pyramid scheme of progressively smaller subnetworks.} \label{fig:tree_example}
	\end{figure*}
\fi

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{random_tree_1}\\
	\includegraphics[width=0.475\textwidth]{random_tree_2}
	\captionspacefig \caption{Random trees with different randomised branching parameters (higher $b$ at the bottom). When a node has zero branches, it terminates the branch. This type of graph topology qualitatively captures the hierarchical, yet ad hoc qualities of many real-world networks, and may act as a useful test model for simulations.} \label{fig:random_tree}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.475\textwidth]{random_tree_1}
	\includegraphics[width=0.475\textwidth]{random_tree_2}
	\captionspacefig \caption{Random trees with different randomised branching parameters (higher $b$ on the right). When a node has zero branches, it terminates the branch. This type of graph topology qualitatively captures the hierarchical, yet ad hoc qualities of many real-world networks, and may act as a useful test model for simulations.} \label{fig:random_tree}
	\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{MST}
\captionspacefig \caption{A random graph (blue) with an MST highlighted (red).} \label{fig:mst}
\end{figure}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.35\textwidth]{percolation_1}\\
	\includegraphics[width=0.35\textwidth]{percolation_2}\\
	\includegraphics[width=0.35\textwidth]{percolation_3}
	\captionspacefig \caption{A square lattice graph subject to different percolation rates (node defects). As the failure rate increases (top to bottom), the larger network segregates into a multipartite graph of smaller disjoint islands (denoted by colour).} \label{fig:perc_graph}\index{Percolation topologies}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.325\textwidth]{percolation_1}
	\includegraphics[width=0.325\textwidth]{percolation_2}
	\includegraphics[width=0.325\textwidth]{percolation_3}
	\captionspacefig \caption{A square lattice graph subject to different percolation rates (node defects). As the failure rate increases (left to right), the larger network segregates into a multipartite graph of smaller disjoint islands (denoted by colour).} \label{fig:perc_graph}\index{Percolation topologies}
	\end{figure*}
\fi

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.325\textwidth]{random_0}\\
	\includegraphics[width=0.325\textwidth]{random_05}\\
	\includegraphics[width=0.325\textwidth]{random_1}
	\captionspacefig \caption{The 15-vertex random graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (top to bottom).} \label{fig:random_graph}\index{Random topologies}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.325\textwidth]{random_0}
	\includegraphics[width=0.325\textwidth]{random_05}
	\includegraphics[width=0.325\textwidth]{random_1}
	\captionspacefig \caption{The 15-vertex random graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (left to right).} \label{fig:random_graph}\index{Random topologies}
	\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{power_law}
\captionspacefig \caption{Examples of the power law, characteristic of the vertex order distribution in scale-free networks.}\label{fig:power_law}\index{Scale-free networks}\index{Power law}	
\end{figure}

@@

A feature of scale-free networks of especial interest in the context of computer networks is their robustness against node failure. Suppose we constructed a percolated (Sec.~\ref{sec:perc_topol}) instance of a typical scale-free network. Such a network is highly robust against node/edge deletions compared to many other graph constructions, in the sense that a relatively large number of failures must occur to disconnect the graph. This makes the scale-free network characteristic a particularly attractive one from the perspective of the failure-tolerance of the network.

Scale-free networks typically exhibit extremely small diameter (average distance between nodes), scaling as \cite{bib:PhysRevLett.90.058701},
\begin{align}
	d = O(\log \log |V|).
\end{align}
That is, they exhibit (exponentially) smaller diameter than tree graphs (which already exhibit only logarithmic depth). Thus, expanding the network (in a manner consistent with the model) by adding a moderate number of new nodes effectively leaves graph diameter unchanged -- the graph diameter is virtually a constant under modest evolution.

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{webgraph_1}\\
	\includegraphics[width=0.475\textwidth]{webgraph_2}
	\captionspacefig \caption{Examples of real-world web-graphs of the internet, capturing their high-level random tree-like structure. Graphics attributed to the Center for Applied Internet Data Analysis (CAIDA), \href{http://www.caida.org}{http://www.caida.org}.}\index{Internet web-graph} \label{fig:webgraph}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.481\textwidth]{webgraph_1}
	\includegraphics[width=0.475\textwidth]{webgraph_2}
	\captionspacefig \caption{Examples of real-world web-graphs of the internet, capturing their high-level random tree-like structure. Graphics attributed to the Center for Applied Internet Data Analysis (CAIDA), \href{http://www.caida.org}{http://www.caida.org}.}\index{Internet web-graph} \label{fig:webgraph}
	\end{figure*}
\fi

@@

The extreme case of network robustness is the complete graph, $K_n$, which has P2P links between every pair of nodes. Therefore, if a single channel fails, there are always alternate paths taking us between nodes. On the opposing extreme are tree graphs, which contain no redundancy whatsoever, and just a single failure will disconnect the network. Scale-free networks sit in the intermediate zone, but are relatively robust against the failure of random nodes/links, but are vulnerable to conspiratorial failures, which target the highly connected hub nodes.

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{graph_deletions_long}
	\captionspacefig \caption{Robustness of network topologies to node and link deletion. Examples of a tree graph (a) and a complete graph, $K_n$, with \mbox{$n=10$} (d). (b,e) The same graphs subject to a single link failure. The failure disconnects the tree graph into a bipartite graph (b), whereas the complete graph's connectivity is unhindered as alternate routes exist between all nodes (e). A single node failure disconnects the tree graph into a $|v|$-partite graph (c), where $|v|$ is the order of the vertex at which failure occurs. The complete graph, on the other hand, is simply reduced to a $K_{n-1}$ graph, with no loss of connectivity (f). Thus, tree graphs are the most vulnerable network topologies to node/link failures, whereas complete graphs are the most robust.}\label{fig:graph_deletions}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=\textwidth]{graph_deletions}
	\captionspacefig \caption{Robustness of network topologies to node and link deletion. Examples of a tree graph (a) and a complete graph, $K_n$, with \mbox{$n=10$} (d). (b,e) The same graphs subject to a single link failure. The failure disconnects the tree graph into a bipartite graph (b), whereas the complete graph's connectivity is unhindered as alternate routes exist between all nodes (e). A single node failure disconnects the tree graph into a $|v|$-partite graph (c), where $|v|$ is the order of the vertex at which failure occurs. The complete graph, on the other hand, is simply reduced to a $K_{n-1}$ graph, with no loss of connectivity (f). Thus, tree graphs are the most vulnerable network topologies to node/link failures, whereas complete graphs are the most robust.}\label{fig:graph_deletions}
	\end{figure*}
\fi

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{K_15}
\captionspacefig \caption{The 15-vertex complete graph, $K_{15}$. Every vertex has an edge to every other, with a total of 105 edges.} \label{fig:complete_graph}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{lattice}
\captionspacefig \caption{A \mbox{$10\times 11$} square lattice graph, and how it might represent a network topology with geographically associated costs. Notice that Hobart has no internet connection (why even include Tasmania at all?).} \label{fig:lattice}
\end{figure}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.325\textwidth]{tree_3_8}\\
	\includegraphics[clip=true, width=0.325\textwidth]{tree_4_8}\\
	\includegraphics[clip=true, width=0.325\textwidth]{tree_5_8}
	\captionspacefig \caption{Balanced tree graphs with branching factor \mbox{$b=8$}, and depths \mbox{$d=3,4,5$}. Despite having no redundant paths, the hierarchical structure of balanced trees somewhat resembles that of real-world networks, which are typically decomposed into a pyramid scheme of progressively smaller subnetworks.} \label{fig:tree_example}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=0.325\textwidth]{tree_3_8}
	\includegraphics[clip=true, width=0.325\textwidth]{tree_4_8}
	\includegraphics[clip=true, width=0.325\textwidth]{tree_5_8}
	\captionspacefig \caption{Balanced tree graphs with branching factor \mbox{$b=8$}, and depths \mbox{$d=3,4,5$}. Despite having no redundant paths, the hierarchical structure of balanced trees somewhat resembles that of real-world networks, which are typically decomposed into a pyramid scheme of progressively smaller subnetworks.} \label{fig:tree_example}
	\end{figure*}
\fi

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{random_tree_1}\\
	\includegraphics[clip=true, width=0.475\textwidth]{random_tree_2}
	\captionspacefig \caption{Random trees with different randomised branching parameters (higher $b$ at the bottom). When a node has zero branches, it terminates the branch. This type of graph topology qualitatively captures the hierarchical, yet ad hoc qualities of many real-world networks, and may act as a useful test model for simulations.} \label{fig:random_tree}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{random_tree_1}
	\includegraphics[clip=true, width=0.475\textwidth]{random_tree_2}
	\captionspacefig \caption{Random trees with different randomised branching parameters (higher $b$ on the right). When a node has zero branches, it terminates the branch. This type of graph topology qualitatively captures the hierarchical, yet ad hoc qualities of many real-world networks, and may act as a useful test model for simulations.} \label{fig:random_tree}
	\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{MST}
\captionspacefig \caption{A random graph (blue) with an MST highlighted (red).} \label{fig:mst}
\end{figure}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.35\textwidth]{percolation_1}\\
	\includegraphics[clip=true, width=0.35\textwidth]{percolation_2}\\
	\includegraphics[clip=true, width=0.35\textwidth]{percolation_3}
	\captionspacefig \caption{A square lattice graph subject to different percolation rates (node defects). As the failure rate increases (top to bottom), the larger network segregates into a multipartite graph of smaller disjoint islands (denoted by colour).} \label{fig:perc_graph}\index{Percolation topologies}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=0.325\textwidth]{percolation_1}
	\includegraphics[clip=true, width=0.325\textwidth]{percolation_2}
	\includegraphics[clip=true, width=0.325\textwidth]{percolation_3}
	\captionspacefig \caption{A square lattice graph subject to different percolation rates (node defects). As the failure rate increases (left to right), the larger network segregates into a multipartite graph of smaller disjoint islands (denoted by colour).} \label{fig:perc_graph}\index{Percolation topologies}
	\end{figure*}
\fi

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.325\textwidth]{random_0}\\
	\includegraphics[clip=true, width=0.325\textwidth]{random_05}\\
	\includegraphics[clip=true, width=0.325\textwidth]{random_1}
	\captionspacefig \caption{The 15-vertex random graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (top to bottom).} \label{fig:random_graph}\index{Random topologies}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=0.325\textwidth]{random_0}
	\includegraphics[clip=true, width=0.325\textwidth]{random_05}
	\includegraphics[clip=true, width=0.325\textwidth]{random_1}
	\captionspacefig \caption{The 15-vertex random graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (left to right).} \label{fig:random_graph}\index{Random topologies}
	\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{power_law}
\captionspacefig \caption{Examples of the power law, characteristic of the vertex order distribution in scale-free networks.}\label{fig:power_law}\index{Scale-free networks}\index{Power law}	
\end{figure}

@@

A feature of scale-free networks of especial interest in the context of computer networks is their robustness against node failure. Suppose we constructed a percolated (Sec.~\ref{sec:perc_topol}) instance of a typical scale-free network. Such a network is highly robust against random node/edge deletions compared to many other graph constructions, in the sense that a relatively large number of failures must occur to disconnect the graph. This makes the scale-free network characteristic a particularly attractive one from the perspective of the failure-tolerance of a network.

Scale-free networks typically exhibit extremely small diameter\index{Graph diameter} (average distance between nodes), scaling as \cite{bib:PhysRevLett.90.058701},
\begin{align}
	d = O(\log \log |V|).
\end{align}
That is, they exhibit (exponentially) smaller diameter than tree graphs (which already exhibit only logarithmic depth). Thus, expanding the network (in a manner consistent with the model) by adding a moderate number of new nodes effectively leaves graph diameter unchanged -- the graph diameter is virtually a constant under modest evolution.

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{webgraph_1}\\
	\includegraphics[clip=true, width=0.475\textwidth]{webgraph_2}
	\captionspacefig \caption{Examples of real-world web-graphs of the internet, capturing their high-level random tree-like structure. Graphics attributed to the Center for Applied Internet Data Analysis (CAIDA), \href{http://www.caida.org}{http://www.caida.org}.}\index{Internet web-graph} \label{fig:webgraph}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=0.481\textwidth]{webgraph_1}
	\includegraphics[clip=true, width=0.475\textwidth]{webgraph_2}
	\captionspacefig \caption{Examples of real-world web-graphs of the internet, capturing their high-level random tree-like structure. Graphics attributed to the Center for Applied Internet Data Analysis (CAIDA), \href{http://www.caida.org}{http://www.caida.org}.}\index{Internet web-graph} \label{fig:webgraph}
	\end{figure*}
\fi

@@

The extreme case of network robustness is the complete graph, $K_n$, which has P2P links between every pair of nodes. Therefore, if a single channel fails, there are \textit{always} alternate paths taking us between nodes. On the opposing extreme are tree graphs, which contain no redundancy whatsoever, and just a single failure will disconnect the network, making certain routes impossible. Scale-free networks sit in the intermediate zone, but are relatively robust against the failure of random nodes/links, but are vulnerable to conspiratorial failures, which target the elite, highly connected hub-nodes.

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{graph_deletions_long}
	\captionspacefig \caption{Robustness of network topologies to node and link deletion. Examples of a tree graph (a) and a complete graph, $K_n$, with \mbox{$n=10$} (d). (b,e) The same graphs subject to a single link failure. The failure disconnects the tree graph into a bipartite graph (b), whereas the complete graph's connectivity is unhindered as alternate routes exist between all nodes (e). A single node failure disconnects the tree graph into a $|v|$-partite graph (c), where $|v|$ is the order of the vertex at which failure occurs. The complete graph, on the other hand, is simply reduced to a $K_{n-1}$ graph, with no loss of connectivity (f). Thus, tree graphs are the most vulnerable network topologies to node/link failures, whereas complete graphs are the most robust.}\label{fig:graph_deletions}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=\textwidth]{graph_deletions}
	\captionspacefig \caption{Robustness of network topologies to node and link deletion. Examples of a tree graph (a) and a complete graph, $K_n$, with \mbox{$n=10$} (d). (b,e) The same graphs subject to a single link failure. The failure disconnects the tree graph into a bipartite graph (b), whereas the complete graph's connectivity is unhindered as alternate routes exist between all nodes (e). A single node failure disconnects the tree graph into a $|v|$-partite graph (c), where $|v|$ is the order of the vertex at which failure occurs. The complete graph, on the other hand, is simply reduced to a $K_{n-1}$ graph, with no loss of connectivity (f). Thus, tree graphs are the most vulnerable network topologies to node/link failures, whereas complete graphs are the most robust.}\label{fig:graph_deletions}
	\end{figure*}
\fi
